In Tables \ref{tab:movielens}, \ref{tab:jester}, and \ref{tab:epinions}, we present the best HR@10 and NDCG@10 scores achieved by each neural recommendation method, including the ensemble learning approach, on the Movielens, Jester, and Epinions datasets, respectively.
Fig. \ref{fig:metrics}, depicts the HR@k and NDCG@k scores while varying k from 1 to 10.
In both the tables and the plots, along with the methods' names we state the most important parameters that we utilized in order to achieve each score.
We refer to the GMF method with embedding size e as GMF(e).
Similarly, we do for the NGCF and CMN approaches.
We refer to the MLP with l layers as MLP(l).
It should be noted, that for the MLP method we follow a tower pattern for the layers as described in Section \ref{sec:models_and_methods}.
Moreover, the size of the embeddings is always set to be half the width of the first layer, while the width of the output layer is fixed to 8.
For the NeuMF approach with embedding size e in the GMF component, and l layers in the MLP component we write NeuMF(e,l).
For all methods that use embedding layers we tried the values e=8,16,32,64 for tuning.
For the MLP and NeuMF approaches we varied the number of layers from 2 to 4.
For the VAE method we used the standard configurations.

\begin{table}[h]
    \centering
    \begin{tabular}{c|c|c}
        \hline
        Movielens & HR@10  & NDCG@10 \\
        \hline
        GMF(32)     & 0.7023 & 0.4202  \\
        MLP(4)      & 0.6616 & 0.3897 \\
        NeuMF(32,2) & 0.7012 & 0.4233 \\
        CMN         & 0.6572&  0.3882 \\
        NGCF(64)    & 0.6937 & 0.4122 \\
        VAE         & 0.7001 & 0.4230 \\
        Ensemble    & 0.8412 & 0.6288
    \end{tabular}
    \caption{Best performance achieved by each method on Movielens dataset.}
    \label{tab:movielens}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{c|c|c}
        \hline
        Jester & HR@10 & NDCG@10 \\
        \hline
        GMF(16)    & 0.8411 & 0.7589 \\
        MLP(3)     & 0.8427 & 0.7569 \\
        NeuMF(8,2) & 0.8404 & 0.7563 \\
        CMN        & $-$ & $-$ \\
        NGCF(32)   & 0.8558	& 0.7615 \\
        VAE        & 0.8482 & 0.7648 \\
        Ensemble   & 0.8802 & 0.7686
    \end{tabular}
    \caption{Best performance achieved by each method on Jester dataset.\\
    {\scriptsize $-$: CMN took 24h for three epochs and did not lead to any useful results}}
    \label{tab:jester}
\end{table}
\begin{table}[h]
    \centering
    \begin{tabular}{c|c|c}
        \hline
        Epinions & HR@10 & NDCG@10 \\
        \hline
        GMF(64)     & 0.2348 & 0.1351 \\
        MLP(2)      & 0.3641 & 0.2135 \\
        NeuMF(32,2) & 0.3750 & 0.2167 \\
        CMN         & 0.1917 & 0.1138  \\
        NGCF(8)     & 0.2226 & 0.1152 \\
        VAE         & 0.3503 & 0.2052 \\
        Ensemble    & 0.3202 & 0.1814
    \end{tabular}
    \caption{Best performance achieved by each method on Epinions dataset.}
    \label{tab:epinions}
\end{table}
\input{src/plots/HR_and_NDCG.tex}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../report"
%%% End:
